---
title: "Example of wiriting probability scores and UMAP coodinates into FCS file as additional channels"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---
This document describes an example for writing both probability scores and UMAP
coodinates int FCS file as additional channels. The exported FCS file can be opened
and viewed in any commercial and in-house flow cytometry software for viewing. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, message = FALSE)
library(flowCore)
source("./utils.R")
```

Load the FCS file that used to generate the csv file used as input for the XGBoost model
```{r}
fcs.files <- "...Path to the fcs file..."
input_fcs <- read.FCS(fcs.files, transformation = F)
```

Load the CSV file outputed from XGBoost model
```{r}
csv.files <- "...Path to the csv file..."
csvdata <- read.csv(file = csv.files, stringsAsFactors = F, row.names = 1)
```

write probability scores and UMAP coodinates into the fcs files
```{r}
f.adding_xgBoost_score(input_fcs = input_fcs, input_csv = csvdata ) 
```


